The pollination trade-off

### 2019-03-14 paper/manuscript.Rmd
Move collinearity results to its own paragraph

@@

We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c). 
In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c). 
The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
Finally, the number of shared pollinators had a negative association with both the absolute and relative amounts of conspecific pollen deposited, but these impacts were small when compared to the other variables. 
Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)), indicating that collinearity did not influence our findings qualitatively.

>>>>

We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c). 
In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c). 
The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
Finally, the number of shared pollinators had a negative and neutral association with conspecific and heterospecific pollen, but these impacts were small when compared to the other variables.

Overall, collinearity did not influence our findings qualitatively.
Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)). 
One exception was visit effectiveness, which exhibits a positive association with the relative amount of conspecific pollen under some variable combinations (all with relatively low AICc support).

@@
